Specific leaf mass explains difference in biomass partitioning between woody plant functional types

### 2014-10-13 manuscript/draftpaper.Rnw
Added tables of counts to manuscript, showing sample sizes used by pft, biome (plants and species)

>>>>

\clearpage
\section{Supporting Tables}

<<results='asis', echo=FALSE>>=
load("tables/Table_counts.RData")
print(xtable(tab_mlfastba, align="rlll|l",
             caption="mlf/asba"
             ), hline.after=c(0,3), caption.placement="top")
@

<<results='asis', echo=FALSE>>=
print(xtable(tab_alfastba, align="rlll|l",
             caption="alf/asba"
             ), hline.after=c(1,3), caption.placement="top")
@

<<results='asis', echo=FALSE>>=
print(xtable(tab_lmf, align="rlll|l",
             caption="LMF"
             ), hline.after=c(1,3), caption.placement="top")
@

<<results='asis', echo=FALSE>>=
print(xtable(tab_lar, align="rlll|l",
             caption="LAR"
             ), hline.after=c(1,3), caption.placement="top")
@
